---
title: 'Casting Multiple Shadows'
subtitle: "high-dimensional interactive data visualisation with tours and embeddings"  
author: "<span style = 'font-size: 90%;'>Stuart Lee, Monash University</span>"
date: "<span style = 'font-size: 90%;'>Final Review<br><br> Tuesday 10th March, 2020 </span> <br><br>"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [saltheme.css, extra.css, animate.css]
    nature:
      ratio: "16:9"
      titleSlideClass: ["left", "middle", "inverse"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true
<div class="my-footer"><span>bit.ly/LINK • @sa-lee</span></div> 

```{r setup, include=FALSE}
# options(htmltools.dir.version = FALSE, width = 120)
# NOTE TO SELF: The CSS styles were created in `create-njt-theme.R`
knitr::opts_chunk$set(
  fig.path = "figures/",
  cache.path = "cache/",
  fig.align = "center",
  fig.width = 13,
  fig.height = 6,
  fig.retina = 3,
  fig.show = "hold",
  external = TRUE,
  # dev = "svglite",
  # dev.args = list(bg = "transparent"),
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  echo = FALSE,
  autodep = TRUE
)
```

```{r library, include = FALSE}
library(vegawidget)
library(htmltools)
library(liminal)
```

```{r helpers, include=FALSE}
mp4_vid <- function(src){
  HTML(
    paste0(
      '<video autoplay>
        <source src="', src, '" type="video/mp4">
      </video>'
    )
  )
}

fig.fullsize <- c(fig.height = 3.5, fig.width = 8, out.width = "150%"
)

as_table <- function(...) knitr::kable(..., format='html', digits = 3)

# **ni**ck's **pa**lette
slpal <- list(red = "#d51d5e",
             orange = "#ffc358",
             blue = "#00CFFF",
             tan = "#D0C1AA",
             light_blue = "#C0DDE1",
             light_tan = "#F2E4DA",
             light_orange = "#fdf4ac",
             light_red = "#D98594",
             pale_blue = "#86C2DA",
             pale_tan = "#fff4dc",
             pale_orange = "#E7C99E",
             pale_red = "#E3A1B8")

```

<!--
talk outline
- review of phd thus far
- the problem
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - quick draw
- future work
-->

---
class: inverse, middle, center

# Intro

---

# Background

---

Put More slides here.

---

# Take homes

---

# Future Directions

.large[
- More features
- More features
- More features
]

---

# Test

.small[small]
.

---

# Thanks

.large.pull-left[
- So many great people
- So many great people
- So many great people
- So many great people
]

.large.pull-right[
- So many great people
- So many great people
- So many great people
- So many great people
]

---

# Resources

.large[
- So many things
- So many things
- So many things
- So many things
]

---

# Colophon

.large[
- Slides made using [xaringan](https://github.com/yihui/xaringan)
- Extended with [xaringanthemer](https://github.com/gadenbuie/xaringanthemer)
- Colours taken + modified from [Kiki's Delivery Service](https://github.com/ewenme/ghibli)
- Header font is **Montserrat**
- Body text font is **Open Sans**
- Code font is **Fira Mono**
]

---

# Learning more

.large[
`r icon::fa_box_open() ` [liminal]()

`r icon::fa('link')` [talk link]()
]


---

.vhuge[
**End.**
]
