---
title: 'Casting Multiple Shadows'
subtitle: "high-dimensional interactive data visualisation with tours and embeddings"  
author: "<span style = 'font-size: 90%;'>Stuart Lee, Monash University</span>"
date: "<span style = 'font-size: 90%;'>Final Review<br><br> Tuesday 10th March, 2020 </span> <br><br>"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [saltheme.css, extra.css, animate.css]
    nature:
      ratio: "16:9"
      titleSlideClass: ["left", "middle", "inverse"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true
<div class="my-footer"><span>bit.ly/LINK • @sa-lee</span></div> 

```{r setup, include=FALSE}
# options(htmltools.dir.version = FALSE, width = 120)
# NOTE TO SELF: The CSS styles were created in `create-sal-theme.R`
knitr::opts_chunk$set(
  fig.path = "img/",
  cache.path = "cache/",
  fig.align = "center",
  fig.width = 13,
  fig.height = 6,
  fig.retina = 3,
  fig.show = "hold",
  external = TRUE,
  # dev = "svglite",
  # dev.args = list(bg = "transparent"),
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  echo = FALSE,
  autodep = TRUE
)
```

```{r library, include = FALSE}
library(vegawidget)
library(htmltools)
library(liminal)
```

```{r helpers, include=FALSE}
mp4_vid <- function(src){
  HTML(
    paste0(
      '<video autoplay>
        <source src="', src, '" type="video/mp4">
      </video>'
    )
  )
}

fig.fullsize <- c(fig.height = 3.5, fig.width = 8, out.width = "150%"
)

as_table <- function(...) knitr::kable(..., format='html', digits = 3)

# palette
slpal <- list(red = "#d51d5e",
             orange = "#ffc358",
             blue = "#00CFFF",
             tan = "#D0C1AA",
             light_blue = "#C0DDE1",
             light_tan = "#F2E4DA",
             light_orange = "#fdf4ac",
             light_red = "#D98594",
             pale_blue = "#86C2DA",
             pale_tan = "#fff4dc",
             pale_orange = "#E7C99E",
             pale_red = "#E3A1B8")

```

<!--
talk outline
- review of phd thus far
- the problem
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - quick draw
- future work

We begin with the data science life cycle  

Add a human in the loop

Zoom on in on the import wrangling

Show the PhD thus far

plyranges 

How plyranges leads to be able to express new types of analyses 

The fluentGenomics paper and the superintronic paper 

Back to the lifecycle 

Zoom in on the visualisation and model side 

In particular we are going to looking embedding algorithms or how we look at high dimensional space 

Briefly describe the overarching goal of these methods 

How are these actually used in people’s work

Cluster orientation

What does that involve?

Identification, shape and verification 

Two tools for looking at this 

Non linear embedding algorithms 
Tours

Zoom in non linear embedding algorithms 

Focus on tSNE

A description of the algorithm 

How does it work

What are the important parameters 

Focus on tour

A description of what it is

How does it work?

The tour demands an interactive framework 

Recasting the tour as a streaming data problem 

How does this work?

Description of the application 

Show a silly example of user interaction with the pollen data 

This gives a simple overview of the interface and API

Our approach: you can have it all

Ensemble graphics 

Interactions 

Brushing and highlighting 

Case study 1: fake trees


Case study 2: quick draw 

Limitations 

Further improvements 

Next steps 

Take homes

-->

---
class: inverse, middle, center

# The story so far...

---




# Background

---

Put More slides here.

---

# Take homes

---

# Future Directions

.large[
- More features
- More features
- More features
]

---

# Test

.small[small]
.

---

# Acknowledgements

.large.pull-left[
- Di Cook
- Matt Ritchie
- Paul Harrison
]

.large.pull-right[
- Ursula Laa
- Nick Tierney
]

---

# Colophon

.large[
- Slides made using [xaringan](https://github.com/yihui/xaringan)
- Extended with [xaringanthemer](https://github.com/gadenbuie/xaringanthemer)
- Colours taken + modified from [Kiki's Delivery Service](https://github.com/ewenme/ghibli)
- Header font is **Montserrat**
- Body text font is **Open Sans**
- Code font is **Fira Mono**
]

---

# Learning more

.large[
`r icon::fa_box_open() ` [liminal](https://github.com/sa-lee/liminal)

`r icon::fa('link')` [talk link]()
]


---

.vhuge[
**End.**
]
